---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

load("data/massmail_data.rda")
knitr::read_chunk("R/01-dependencies.R")
knitr::read_chunk("R/02-data-manipulation.R")
knitr::read_chunk("R/03-ggplot-covid19-msg.R")
knitr::read_chunk("R/04-wordcloud.R")
```

```{r pkg-dependencies, include = FALSE, echo = FALSE, message=FALSE} 
```

# massmail

<!-- badges: start -->
[![Data build status](https://github.com/illinois-r/massmail/workflows/data-refresh/badge.svg)](https://github.com/illinois-r/massmail/actions)
<!-- badges: end -->

The goal of the massmail repository is to provide access to the mass mailing 
archives at the University of Illinois at Urbana-Champaign (UIUC). Each time
the University sends an e-mail en-mass to community members its contents, 
time, and recipient number is recorded publicly. The archive may be viewed 
here:

<https://massmail.illinois.edu/massmailArchive>

Data has **`r nrow(massmail_data)`** observations and **`r ncol(massmail_data)`** variables:

- `datetime`: Date and time when the email was sent in the form of `YYYY-MM-DD HMS` 
  with either CDT or CST.
- `date`: Date when the email was sent in the form of `YYYY-MM-DD`.
- `time`: Time when the email was sent in the form of a 24 hour clock with `HH:MM`.
- `sent`: Number of recipients of the massmail.
- `subject`: Text displayed in the email subject line
- `url`: Link to the official email in the massmail archive.
- `content`: Contents of the email without html markup.

**Sample**

```{r show-preview, echo = FALSE, message = FALSE}
```

**Email Contents**

```{r show-email, echo = FALSE}
```

Data is made available under two file formats:

- CSV: [`massmail_data.csv`](data/massmail_data.csv)
- RDA: [`massmail_data.rda`](data/massmail_data.rda)

To read in the files use either:

**R**

```r
# Process data from CSV
massmail_data = readr::read_csv(
  "https://raw.githubusercontent.com/coatless/massmail/master/data/massmail_data.csv"
)

# Loads as massmail_data without needing a layer of processing
url = "https://raw.githubusercontent.com/coatless/massmail/master/data/massmail_data.rda"
download.file(url, basename(url))
load(basename(url))
```

**Python**

```python
# Import pandas library
import pandas as pd

# Load data into pandas
massmail_df = pd.read_csv(
  'https://raw.githubusercontent.com/coatless/massmail/master/data/massmail_data.csv'
)
```

The data scraping, cleaning, and importation script steps were written in _R_
and can be found at [`data-raw/01-setup-mass-mail.R`](data-raw/01-setup-mass-mail.R).

## Sample Data Usage


### R Package Dependencies

```{r pkg-dependencies, message = FALSE, warning = FALSE, eval = FALSE} 
```

### Data Load and Manipulation

```{r data-load, message = FALSE, warning = FALSE} 
```

### Massmail Frequency Graphs

```{r sample-graphic, message = FALSE, warning = FALSE} 
```

### Massmail Message Contents

```{r email-body-txt}
```

#### Most popular words

```{r most-popular-words, warning=FALSE}
```

#### Wordcloud

```{r word-cloud, warning=FALSE}
```



## Acknowledgements

The idea to scrap the mass mail archive arose after reading a post by
[`/u/grigorescu`](https://www.reddit.com/user/grigorescu/) titled [Wordcloud from the 35 COVID-related Massmails sent so far...](https://www.reddit.com/r/UIUC/comments/fudk9w/wordcloud_from_the_35_covidrelated_massmails_sent/)
on [`r/uiuc`'s subreddit](https://www.reddit.com/r/UIUC). The user made
the [wordcloud by copying and pasting contents](https://www.reddit.com/r/UIUC/comments/fudk9w/wordcloud_from_the_35_covidrelated_massmails_sent/fmc71es/) from the massmail archive into <https://www.wordclouds.com/>.

## Author

James Joseph Balamuta

## License

GPL (>= 2)
